An iterated Grothendieck construction of semi-cubical types

### 2022-02-19 paper/paper.tex
CubeInfinity: introduce something with a bombastic name ;)

\begin{listing}[H]
  \begin{minted}{coq}
    (* PartialBox consists of an 0-cells, and fillers which are the 1-cells,
    2-cells, and 3-cells relating the different 0-cells on the cube  *)
    Record PartialBoxBase (n : nat) (csp : Type@{l'}) := {
      box' {p} (Hp : p.+1 <= n) : csp -> Type@{l} ;
      (* [box' n D] is [box (n-1) D.1] *)
      box'' {p} (Hp : p.+2 <= n) : csp -> Type@{l} ;
      subbox' {p q} {Hp : p.+2 <= q.+2} (Hq : q.+2 <= n) (ε : side) {D : csp} :
        box' (↓ (Hp ↕ Hq)) D -> box'' (Hp ↕ Hq) D;
    }.

@@

    Definition mkPB {n} {C : Cubical n} :
      PartialBoxBase n.+1 mkcsp := {|
      box' {p} {Hp : p.+1 <= n.+1} {D : mkcsp} := C.(Box).(box) (⇓ Hp) D.1 ;
      box'' {p} {Hp : p.+2 <= n.+1} {D : mkcsp} := C.(PB).(box') (⇓ Hp) D.1 ;
      subbox' {p q} {Hp : p.+2 <= q.+2} {Hq : q.+2 <= n.+1} {ε} {D : mkcsp} {d} :=
        C.(Box).(subbox) (Hp := ⇓ Hp) (⇓ Hq) ε d ;
    |}.

    Definition mkBox {n} {C : Cubical n} p : PartialBox n.+1 p mkcsp mkPB.
      induction p as [|p (boxSn, subboxSn, cohboxSn)].
      + (* ... *)
  \end{minted}
\end{listing}

>>>>

\begin{listing}[H]
  \begin{minted}{coq}
    Record PartialBoxPrev (n : nat) (csp : Type@{l'}) := {
      box' {p} (Hp : p.+1 <= n) : csp -> Type@{l} ;
      (* [box' n D] is [box (n-1) D.1] *)
      box'' {p} (Hp : p.+2 <= n) : csp -> Type@{l} ;
      subbox' {p q} {Hp : p.+2 <= q.+2} (Hq : q.+2 <= n) (ε : side) {D : csp} :
        box' (↓ (Hp ↕ Hq)) D -> box'' (Hp ↕ Hq) D;
    }.

@@

    Definition mkBoxPrev {n} {C : Cubical n} :
      PartialBoxBase n.+1 mkcsp := {|
      box' {p} {Hp : p.+1 <= n.+1} {D : mkcsp} := C.(Box).(box) (⇓ Hp) D.1 ;
      box'' {p} {Hp : p.+2 <= n.+1} {D : mkcsp} := C.(PB).(box') (⇓ Hp) D.1 ;
      subbox' {p q} {Hp : p.+2 <= q.+2} {Hq : q.+2 <= n.+1} {ε} {D : mkcsp} {d} :=
        C.(Box).(subbox) (Hp := ⇓ Hp) (⇓ Hq) ε d ;
    |}.

    Definition mkBox {n} {C : Cubical n} p : PartialBox n.+1 p mkcsp mkPB.
      induction p.
      + (* ... *)
  \end{minted}
\end{listing}
